Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-06 paper/paper.Rmd
ask for clarification of scattered appearance
request to clearly state that buffering could have also been put into the spatiotemporal category

Buffering is mostly applied in the coordinate space due to the scattered appearance of observations in this space.
However, there is no practical limitation that would prevent this method to be applied in a 2D + time setting.
Because \pkg{mlr3spatiotempcv} supports two spatial-only "buffering" implementations, (1) "Spatial buffering" from package \pkg{blockCV} and (2) "Leave-one-disc-out cross-validation" from \pkg{sperrorest}, buffering was attributed to the category of spatial partitioning methods.

>>>>

<!--JM: not entirely sure what scattered appearance refers to-->
Buffering is most often applied in coordinate space due to the scattered appearance of observations in this space.
However, this method could be easily extended to a 2D + time setting.
<!-- JM: I guess you mean that you could have placed buffering also into spatiotemporal partition. I would advise to say so instead of letting the reader guess.-->
Since \pkg{mlr3spatiotempcv} supports two spatial-only "buffering" implementations, (1) "Spatial buffering" from package \pkg{blockCV} and (2) "Leave-one-disc-out cross-validation" from \pkg{sperrorest}, buffering was attributed to the category of spatial partitioning methods.
